From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-02 Pi+/paper/finite.tex
Fix uses of downf function

\begin{definition}[$\downf : (n : \Nat) \to (k : \Nat) \to {\List[\Fin[\suc[k + n]]]}$]
  \begin{align*}
    n \downf \zero   & \defeq \nil                       \\
    n \downf \suc[k] & \defeq (k + n) \cons (n \downf k)
  \end{align*}
\end{definition}

The result of this function is the sequence \(k + n, k + n - 1, k + n - 2, \ldots, n + 1\). Since we think of the number
$m$ as the transposition $\tau_m$ which swaps elements $\el{m}$ and $\el{m+1}$, the role of this helper function is to
produce a sequence of transpositions -- a permutation -- which moves element $\el{k + n}$ $k$ places left, shifting all
the elements in between one place right. Expressed in terms of the braiding diagram, for $n = 0$ and $k = 4$, it has the
following form:

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 2$ and $k = 4$, it allows for
the reduction $[7, 6, 5, 4, 3, 7] \longcox* [6, 7, 6, 5, 4, 3]$. Visualised on the braid diagram, it looks as follows:

@@

\begin{definition}[$\immersion : (n : \Nat) \to {\Lehmer[n]} \to {\List[\Fin[n]]}$]
  \begin{align*}
    \immersion(\zero, \zero)    & \defeq \nil                                              \\
    \immersion(\suc[n], (r, l)) & \defeq \immersion(n, l) \append ((\suc[n] - r) \downf r)
  \end{align*}
\end{definition}

As described above, the number $r$ at the position $k$ in the tuple describes how many inversions the element $\el{k}$
has. Thus, we need to perform $r$ many adjacent transpositions to get to the desired position. The function that
constructs a sequence of $r$ adjacent transpositions $[\suc[n], \suc[n] - 1, \suc[n] - 2, \ldots \suc[n] - r]$ is
$(\suc[n] - r) \downf r$.

>>>>

\begin{definition}[$\downf : (n : \Nat) \to (k : \Nat) \to {\List[\Fin[k + n]]}$]
  \begin{align*}
    n \downf \zero   & \defeq \nil                       \\
    n \downf \suc[k] & \defeq (k + n) \cons (n \downf k)
  \end{align*}
\end{definition}

The result of this function is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\). Since we think of the
number $m$ as the transposition $\tau_m$ which swaps elements $\el{m}$ and $\el{m+1}$, the role of this helper function
is to produce a sequence of transpositions -- a permutation -- which moves element $\el{k + n}$ $k$ places left,
shifting all the elements in between one place right. Expressed in terms of the braiding diagram, for $n = 0$ and $k =
  4$, it has the following form:

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 2$ and $k = 3$, it allows for
the reduction $[6, 5, 4, 3, 2, 6] \longcox* [5, 6, 5, 4, 3, 2]$. Visualised on the braid diagram, it looks as follows:

@@

\begin{definition}[$\immersion : (n : \Nat) \to {\Lehmer[n]} \to {\List[\Fin[\suc[n]]]}$]
  \begin{align*}
    \immersion(\zero, \zero)    & \defeq \nil                                              \\
    \immersion(\suc[n], (r, l)) & \defeq \immersion(n, l) \append ((\suc[n] - r) \downf r)
  \end{align*}
\end{definition}

As described above, the number $r$ at the position $k$ in the tuple describes how many inversions the element $\el{k}$
has. Thus, we need to perform $r$ many adjacent transpositions to get to the desired position, which is given by
$(\suc[n] - r) \downf r$.
